The necessity of hypermedia RDF and an approach to achieve it

### 2012-04-12 eswc-2012/workshop2.tex
more on HATEOAS
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@216 43ef1190-90fd-4dd7-a769-d0121f02b80e

% TODO:
% Explain HATEOAS
% More on new H-factors
% References
% POST in relation to graph store
% Weakness of RDF

@@

In a read-only situation, the HATEOAS constraint requires that the
application can navigate from one resources to another using the
hypermedia links in the present resource \emph{only}, they should not
require any out-of-band information.

>>>>

% TODO:
% Explain HATEOAS
% More on new H-factors
% References
% POST in relation to graph store
% Weakness of RDF
% Reformulate something on SPARQL about enabling

@@

In a read-only situation, the HATEOAS constraint requires that the
application can navigate from one resources to another using the
hypermedia links in the present resource \emph{only}, they should not
require any out-of-band information. It is very common that
specifications that advertise themselves as RESTful has a read-write
API that is specified in terms of URI structure as well as HTTP
verbs. This is not a violation of the HATEOAS constraint \textit{per
  se}, but it would usually be superfluous as the same information
\emph{must} be available in a hypermedia message in order to satisfy
the HATEOAS constraint. The constraint does not require this
information to be available in \emph{all} messages, nor does it
require that all resources can be reached from any other resource, and
so, it is not a very strict constraint.
